Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-03-05 ongoing/report/1_introduction.tex
Reformatting source

\m{\Nm{a}} denotes the magnitude for real or complex numbers \m{a}.
The real and imaginary part of \m{a} will be denoted respectively as \m{\MF{Re} (a)} and \m{\MF{Im} (a)}, respectively, thus \m{a =\MF{Re} (a) + i \MF{Im} (a)}

We restrict our discussion to \m{\MB{R}^N} or \m{\MB{C}^N} seen as the Hilbert space , equipped with standard inner product.
Lower case Latin alphabets with single underline, like \m{\V{a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m{\M{A}}, denote matrices.
Particularly, define \m{\V{1} =\IP {1, \dots, 1}} and \m{\V{1} =\IP {1, \dots, 1}}.

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m{\MB{R}^N} is over field \m{\MB{R}}, and that on \m{\MB{C}^N} is over field \m{\MB{C}}.
We use \m{\MB{K}} to refer to either \m{\MB{R}} or \m{\MB{C}}.
Not to avoid confusion, we call the Hilbert space \m{\MB{K}^N} over \m{\MB{K}} to be \m{\MB{V}_{\MB{K}} (N)}.
We also call the collection of \m{M} by \m{N} matrices to be \m{\MB{M}_{\MB{K}} (M,N)}, and its role as linear transformation is understood.
Inner product of \m{\V{a}} and \m{\V{b}} is denoted as \m{\IP{ \V{a}, \V{b} }}.
Slightly abusing notation, we denote as \m{\V{a} (n)} the \m{n}-th component of \m{\V{a}}, and denote as \m{\V{A} (m,n)} the \m{(m,n)}-entry of \m{\V{A}}
Particularly, \m{\V{u}_n} is the \m{n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\m{\VNm {\V{a}} _p} denotes the \m{\ell_p}-norm of vector \m{\V{a}}.
Recall that \m{\ell_\infty}-norm is the maximum-magnitude norm.

Denote as \m{\MB{P} (X)} the probability, and \m{\MB{E} (X)} the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
In vague terms, the capacity \m{C} of a MIMO channel \m{\M{H}} at perfect channel state information is well-known to be roughly in the form \m{\log \det (I +\RM{SNR})}, but that knowledge is hardly always available.
What makes things more difficult is the case that \m{\M{H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m{\log \det (I +\RM{SNR})}.

Therefore the real-time estimation, \m{\hat{\M{H}}}, of \m{\M{H}} is of paramount importance.
Needless to say, when the \m{\hat{\M{H}}} is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithms also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus necessary.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m{N_p \in \MB{N}} is much larger than the number of measurements \m{N_m \in \MB{N}}, namely,
%
\Disp{
\NC N_p \gg N_m \NR
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m{N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m{\ell_1} minimization program.
The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.

Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m{\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
In addition, they derived a probability bound of mean suqare error, showing the probability of successful recovery is overwhelming.

From the realistic perspective, the formulation as an \m{\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

In this article we focuss on DS, and we introduce several notions before we describe their work.
To facilitate reader's understanding, in this section we will consistently use \m{N_p} and \m{N_m} to denote matrix dimensions.
Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.

We will use \m{T \RB{N_m} =\{1, \dots, N_m\}} to denote the support of \m{\MB{V}_{\MB{K}} (N_m)}.

\Result
{Definition}
{
Suppose \m{\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)}.
Let \m{\MC{T} \subset T \RB{N_p}}.
Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
}

\Result
{Definition}
{
\m{x \in \MB{V}_{\MB{K}} (N_m)} is called \m{s}-sparse with support \m{\MC{A}}, \m{s <N_m}, if there is \m{\MC{A} \subset T \RB{N_m}} such that
%
\Disp{ 
\NC x_{T(N) -\MC{A}}
=\NC \V{0} \NR
}
with
\Disp{ 
\NC \# \MC{A} \leq s. \NR
}
That is, only at most \m{s} components of \m{x} is nonzero.
}

\Result
{Program}
{
Let \m{P \in \MB{M}_\MB{K} (N_m, N_p)} and \m{y \in \MB{V}_\MB{K} (N_p)} be given.
Find \m{h \in \MB{V}_\MB{K} (N_p)} with
%
\Disp{
\NC
h
= \NC \startcases
\NC \Min {h'}
\quad \MC \VNm {h'} _1 \NR[+]
\NC \RM{subject}\; \RM{to}
\quad \MC P h' =y \NR
\stopcases \NR
}
}

Now let \m{y =P h}.
Suppose \m{h} is \m{s}-sparse, then the program () completely recovers \m{h}.
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m{\ell_1}-minimization program with an overwhelming probability.

\Result
{Definition}
{
Consider \m{P \in \MB{M}_{\MB{K}} (N_m, N_p)}, with unity-\m{\ell_2}-norm columns.
For \m{s =1, \dots N_p}, we say that \m{P} satisfies the restricted isometry property (RIP) of sparsity \m{s} with respect to \m{0 \leq \d_s \leq 1}, if, for all \m{s}-sparse \m{\V{x} \in \MB{V}_{\MB{K}} (N_p)}, for all \m{\MC{T} \subset T(N_m)} with \m{\#\{\MC{T}\} \leq s},
%
\Disp{
\NC \NC (1-\d_s) \VNm {V{x}}^2 \NR
\NC \leq \NC \VNm {P_{\MC{T}} \V{x}} _2^2 \NR
\NC \leq \NC (1+\d_s) \VNm {\V{x}} _2^2 \NR[+]
}
}

RIP is essentially saying that \m{P} is ``almost unitary'' up to ``relative error'' \m{\d_s}.

Now, consider a linear transformation with noise corruption,
%
\Disp{
\NC \V{y} =\M{P} \V{h} + \V{z} \NR
}
%
where (w.l.o.g.) \m{z} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m{h} when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \m{\M{P} \in \MB{V}_\MB{R} (N_m, N_p)} and \m{\V{y} \in \MB{V}_\MB{R} (N_m)} be given.
Find \m{\V{h} \in \MB{V}_\MB{R} (N_m)} by
%

\Disp{
\NC \V{h}
=
\NC \startcases
\NC \Min {\V{h}'} \quad \MC \VNm {\V{h}'} _1 \NR
\NC \RM{subject}\; \RM{to} \quad \MC \VNm {\M{P}^\H (\M{P} \V{h} -\V{y})} _\infty \leq \gamma \NR
\stopcases \NR
}
}

They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
And it can be shown that this \m{\ell_1}-minimization problem with \m{\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
Note that they confined their discussion for real vectors.

@@

The constant \m{\d} in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \m{\d=0}, i.e., that \m{P} is fully unitary, rendering the RIP an important role.
Here, it is not clear at first what matrices serves as the RIP condition.

@@

\Result
{Theorem}
{
Let each entry of random matrix \m{P \in \MB{M}_\MB{K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m{\pm 1/\R{N_m}} (that is, Rademacher distribution).
Then, with \m{0 <\epsilon <1},
%
\Disp{
\NC \NC \MB{P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm{h} _2^2) \NR
\NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
}
}

@@

One of the first papers, Bajwa et.\ al.\ (2010) argues the \m{\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m{X} is RIP for overwhelming probability, providing the ground for the former paper.

To explain the idea, consider a linear time-invariant channel that \m{y(t) =(x \star h)(t) + z(t)}, where \m{h(t)} is the channel's impulse response, \m{y(t)} is the output, and, for each time index, \m{x(t)} is i.i.d.\ Rademacher, and \m{z(t)} is i.i.d.\ Gaussian.
Simply assuming \m{h} has sparse support, and let the convolution with \m{x} be expressed by a matrix \m{X}, \m{X} is a Toeplitz matrix, so that \m{y =X h +z}.
Then Bajwa et.\ al.\ was able to show that, \m{X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

@@

Same as before, consider \m{\V{y} \in \MB{V}_\MB{K} (N_p)}, \m{\V{h} \in \MB{V}_\MB{K} (N_s)}, where \m{\V{h}} is \m{s}-sparse, with \m{N_p \gg N_s}.
If
\Disp{
\NC \V{y} =\M{P} \V{h}, \NR
}
that is, the noiseless, real-number case.
We pick up the columns of \m{\M{P}} greedily, hoping to correspond to the support of \m{\V{h}}, thus recovering the original signal.

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m{0 <\d <1},
%
\Disp{
\NC M \geq 16s \log (N/\d) \NR
}
%
Then OMP (Algorithm \_\_) recovers \m{x} completely, with overwhelming probability \m{1-\d}.
}

@@

For concreteness, let \m{\M{F}} be the precoder and \m{\M{W}} the combiner, and \m{\M{H}} the channel, and consider the noiseless case.
Let signal \m{\V{x}} be sent, and \m{\V{y}} be receiverd, that is
%
\Disp{
\NC \V{y} =\M{W} \M{H} \M{F} \V{x} \NR
}
%

\Result
{Definition}
{
Define \m{\RM{vec} (\M{A}) \in \MB{K}^{NM}} to be the vectorization of \m{\M{A} \in \MB{M}_{\MB{K}} (N,M)}.
}

\Result
{Definition.}
{
For \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)} and \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)}
Define the Kronecker product \m{\RM{vec} (A) \in \MB{K}^{nm}} 
}

With (), scholars often exploit the relation
%
\Disp{
\NC \RM{vec} (Y)
=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H}) \NR
}
%

>>>>

\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} (a)} and \m {\MF {Im} (a)}, respectively, thus \m {a =\MF {Re} (a) + i \MF {Im} (a)}

We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
Particularly, define \m {\V {1} =\IP {1, \dots, 1}}.
Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {(m,n)}-th entry of \m {\M {A}}.

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} (N)}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} (M,N)}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} (n)} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} (m,n)} the \m {(m,n)}-entry of \m {\V {A}}
Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

Denote as \m {\MB {P} (X)} the probability, and \m {\MB {E} (X)} the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

Round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments.

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det (I +\RM {SNR})}, but that knowledge is hardly always available.
What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det (I +\RM {SNR})}.

Therefore the real-time estimation, \m {\hat {\M {H}}}, of \m {\M {H}} is of paramount importance.
Needless to say, when the \m {\hat {\M {H}}} is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithms also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus necessary.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
%
\Disp {
\NC N_p \gg N_m \NR
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m {\ell_1} minimization program.
The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.

Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
In addition, they derived a probability bound of mean suqare error, showing the probability of successful recovery is overwhelming.

From the realistic perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

In this article we focuss on DS, and we introduce several notions before we describe their work.
To facilitate reader's understanding, in this section we will consistently use \m {N_p} and \m {N_m} to denote matrix dimensions.
Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.

We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} (N_m)}.

\Result
{Definition}
{
Suppose \m {\M {A} \in \MB {M}_{\MB {K}} (N_m, N_p)}.
Let \m {\MC {T} \subset T \RB {N_p}}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
}

\Result
{Definition}
{
\m {x \in \MB {V}_{\MB {K}} (N_m)} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
%
\Disp { 
\NC x_{T(N) -\MC {A}}
=\NC \V {0} \NR
}
with
\Disp { 
\NC \# \MC {A} \leq s. \NR
}
That is, only at most \m {s} components of \m {x} is nonzero.
}

\Result
{Program}
{
Let \m {P \in \MB {M}_\MB {K} (N_m, N_p)} and \m {y \in \MB {V}_\MB {K} (N_p)} be given.
Find \m {h \in \MB {V}_\MB {K} (N_p)} with
%
\Disp {
\NC
h
= \NC \startcases
\NC \Min {h'}
\quad \MC \VNm {h'} _1 \NR[+]
\NC \RM {subject} \; \RM {to}
\quad \MC P h' =y \NR
\stopcases \NR
}
}

Now let \m {y =P h}.
Suppose \m {h} is \m {s}-sparse, then the program () completely recovers \m {h}.
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m {\ell_1}-minimization program with an overwhelming probability.

\Result
{Definition}
{
Consider \m {P \in \MB {M}_{\MB {K}} (N_m, N_p)}, with unity-\m {\ell_2}-norm columns.
For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} (N_p)}, for all \m {\MC {T} \subset T(N_m)} with \m {\#\{\MC {T} \} \leq s},
%
\Disp {
\NC \NC (1-\d_s) \VNm {V {x}}^2 \NR
\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
\NC \leq \NC (1+\d_s) \VNm {\V {x}} _2^2 \NR[+]
}
}

RIP is essentially saying that \m {P} is ``almost unitary'' up to ``relative error'' \m {\d_s}.

Now, consider a linear transformation with noise corruption,
%
\Disp {
\NC \V {y} =\M {P} \V {h} + \V {z} \NR
}
%
where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {h} when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \m {\M {P} \in \MB {V}_\MB {R} (N_m, N_p)} and \m {\V {y} \in \MB {V}_\MB {R} (N_m)} be given.
Find \m {\V {h} \in \MB {V}_\MB {R} (N_m)} by
%

\Disp {
\NC \V {h}
= \NC \startcases
\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H (\M {P} \V {h} -\V {y})} _\infty \leq \gamma \NR
\stopcases \NR
}
}

They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
And it can be shown that this \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
Note that they confined their discussion for real vectors.

@@

The constant \m {\d} in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \m {\d=0}, i.e., that \m {P} is fully unitary, rendering the RIP an important role.
Here, it is not clear at first what matrices serves as the RIP condition.

@@

\Result
{Theorem}
{
Let each entry of random matrix \m {P \in \MB {M}_\MB {K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
Then, with \m {0 <\epsilon <1},
%
\Disp {
\NC \NC \MB {P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2) \NR
\NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
}
}

@@

One of the first papers, Bajwa et.\ al.\ (2010) argues the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.

To explain the idea, consider a linear time-invariant channel that \m {y(t) =(x \star h)(t) + z(t)}, where \m {h(t)} is the channel's impulse response, \m {y(t)} is the output, and, for each time index, \m {x(t)} is i.i.d.\ Rademacher, and \m {z(t)} is i.i.d.\ Gaussian.
Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

@@

Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} (N_p)}, \m {\V {h} \in \MB {V}_\MB {K} (N_s)}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
If
\Disp {
\NC \V {y} =\M {P} \V {h}, \NR
}
that is, the noiseless, real-number case.
We pick up the columns of \m {\M {P}} greedily, hoping to correspond to the support of \m {\V {h}}, thus recovering the original signal.

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m {0 <\d <1},
%
\Disp {
\NC M \geq 16s \log (N/\d) \NR
}
%
Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
}

@@

For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
%
\Disp {
\NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
}
%

\Result
{Definition}
{
Define \m {\RM {vec} (\M {A}) \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} (N,M)}.
}

\Result
{Definition.}
{
For \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)} and \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)}
Define the Kronecker product \m {\RM {vec} (A) \in \MB {K}^{nm}} 
}

With (), scholars often exploit the relation
%
\Disp {
\NC \RM {vec} (Y)
=\big[ (F^\H) \otimes W \big] \RM {vec} (\M {H}) \NR
}
%
